Title

### 2013-01-30 inc/photocathode/este/este.tex
typo

The dependence of $\Delta p_x$ on $m^*$ is readily explained through a consideration of energy and momentum conservation in transmission across a boundary with a potential step associated with the effective photoelectric work function $\phi$.
Inside the material, an electron with an energy $E$ greater than $\phi$ has a maximum momentum of $\sqrt{2 m^* (E-\phi) }$ parallel to the boundary if it is to be emitted.
As this momentum component is conserved in emission from the material surface into the vacuum, the rms transverse momentum $\Delta p_x$ of the electron source clearly must scale with $\sqrt{m_*}$ as observed in the experiment.
This is, of course, the \textit{sine qua non} of angle-resolved photoemission studies\cite{himpsel_angle-resolved_1983} where determination of the electron emission angle and energy allows the effective mass parallel to the sample surface to be determined.
We note that the electron effective mass also causes the narrow emission cone reported for $p$-type GaAs(100) negative electron affinity photocathodes\cite{liu_narrow_2005}, where surface cesiation lowers the vacuum level below the $\Gamma_6$-valley minimum ($m^* = 0.067m_0$)  to allow for direct emission of electrons excited into the conduction band.
For direct single-photon photoemission, we would therefore also expect to require that the expression describing the rms transverse momentum to be written as $\Delta p_x = \sqrt{m^* ( \hbar \omega - \phi ) / 3 }$.
Efforts are currently underway to determine if this is indeed the case using a variety of metal photocathodes and the $\sim$ps, 261nm laser radiation source.

>>>>

The dependence of $\Delta p_x$ on $m^*$ is readily explained through a consideration of energy and momentum conservation in transmission across a boundary with a potential step associated with the effective photoelectric work function $\phi$.
Inside the material, an electron with an energy $E$ greater than $\phi$ has a maximum momentum of $\sqrt{2 m^* (E-\phi) }$ parallel to the boundary if it is to be emitted.
As this momentum component is conserved in emission from the material surface into the vacuum, the rms transverse momentum $\Delta p_x$ of the electron source clearly must scale with $\sqrt{m^*}$ as observed in the experiment.
This is, of course, the \textit{sine qua non} of angle-resolved photoemission studies\cite{himpsel_angle-resolved_1983} where determination of the electron emission angle and energy allows the effective mass parallel to the sample surface to be determined.
We note that the electron effective mass also causes the narrow emission cone reported for $p$-type GaAs(100) negative electron affinity photocathodes\cite{liu_narrow_2005}, where surface cesiation lowers the vacuum level below the $\Gamma_6$-valley minimum ($m^* = 0.067m_0$)  to allow for direct emission of electrons excited into the conduction band.
For direct single-photon photoemission, we would therefore also expect to require that the expression describing the rms transverse momentum to be written as $\Delta p_x = \sqrt{m^* ( \hbar \omega - \phi ) / 3 }$.
Efforts are currently underway to determine if this is indeed the case using a variety of metal photocathodes and the $\sim$ps, 261nm laser radiation source.
